---
title: "Chen_Fusarium"
author: "Hypermorphs"
date: "November 19, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# QTL Mapping in ICIMapping  
# ICIMapping v3.2 was downloaded from http://www.isbreeding.net/software/default.aspx?type=detail&id=3
# .bip data files were provided for upload to ICIMapping 
# The mapping method Inclusive Composite Mapping (ICIM) was used for POP1 and POP2
# The mapping method Single marker (SM) analysis was used for POP3 and POP4
# For ICIM, a step size of 1cM was used
# A lod threshold of 2.5 was used for all 4 populations




#### QTL Mapping in R/QTL 
# Tutorial used for R/QTL mapping:  http://www.rqtl.org/rqtltour.pdf
# Four data files were used for mapping in R/QTL:
# ChenPop1.csv, ChenPop2.csv, ChenPop3.csv and ChenPop4.csv
```{r}

if (!require("qtl")) install.packages("qtl")

library(qtl)                                   #Load the R/qtl library

POP <- read.cross("csv", ".", "ChenPop1.csv")  # read in phenotype & genotype data file

POP <- jittermap(POP)                          # so no two markers on top of each other

summary(POP)                                   # provide information about dataset
```





```{r}

plotMissing(POP)                                # examine pattern of missing data
```
```{r}
gt <- geno.table(POP)  

gt[gt$P.value < 0.05/totmar(POP),]                 # QC data by checking alleles for each marker
```

*** QTL mapping ***
- uses hidden Markov model (HMM) for QTL genotype probability calculation
```{r}

POP <- calc.genoprob(POP, step=1, error.prob=0.01)  # step size set to 1cM

out.hk <- scanone(POP, method="hk")                 # single QTL genome scan with Haley-Knott regression

summary(out.hk, threshold=2.5)                      # displays maximum LOD score for each chromosome, with a min of LOD 2.5

operm.hk <- scanone(POP, method="hk", n.perm=1000)  # permutation to determine LOD threshold

summary(operm.hk, alpha=0.05)                       # LOD threshold output

plot(out.hk)                                        # Plot QTL
```









