---
title: "Untitled"
author: "musimwa"
date: "December 5, 2018"
output: html_document
---


```{r}
geno <- read.delim("GenotypeHapmap.txt", h=T, sep = "\t",stringsAsFactors = F, check.names = F, skip = 1, na.strings = NA)


```

#TRANSFORMING INTO MATRIX

```{r}
geno <- as.matrix(geno)
```



#size of matrix dim(geno)

#RANDOMLY SELECTING 2000 MARKERS
```{r}
seed = 1 length(sample(2:dim(geno)[2],53103,replace=F))geno2 <- geno[,-sample(2:dim(geno)[2],53103,replace=F)] dim(geno2)

The new data now (geno 2), has just 2000 markers and 854 individuals

```


#REPLACING NA WITH -9

```{r}
i = 2 j = 1 for (i in i:dim(geno2)[2]){ j = 1 for (j in j:dim(geno2)[1]){ if (is.na(geno2[j,i] == TRUE)){ geno2[j,i] <- -9}}}
```



#THEN I ADDED ANOTHER COLUMN TO INDICATE THE FAMILY. I SCORED ALL IMDIVIDUALS AS 1.

```{r}
geno2 <- cbind(geno2, 1) dim(geno2)
```




#ORDERING COLUMNS

```{r}
geno <- geno2[,c(1,2002,2:2001)]
```



#DUPLICATION OF FILES



```{r}
geno_final <- geno
```

#Structure requires repetitions from a given individual based on the ploidy level. For example, since this is a dipolid species, I duplicated each of the inbred lines and ordered them by their name. By doing that,the file will have twice the numbers of individual in rows.

```{r}

geno_final <- geno[rep(1:nrow(geno), times = 2), ] geno_final <- geno_final[order(geno[,1]),]
```


#The name of the markers were complicated,which could pose a problem in structure.I replaced the markers names by SNP_1, SNP_2,..............

```{r}
colnames(geno_final) <- c("","",paste("SNP", seq(1:2000), sep = "_"))

geno_final <- as.matrix(geno_final)
```



#Export from R into excel

```{r}
write.table(teste2, "structure_duplicate.txt", sep = " ", dec = ",", row.names = FALSE)
```



#Excel

Open the file "structure_duplicate.txt) and save it



